\newpage
\section{Troubleshooting \& Support}

Throughout the design of this program, there may be bugs that might have been an oversight. Troubleshooting continues to become a problem and in the test that was conducted for user experience, the main error issue that exists is logging into the UMS.  These bugs may require troubleshooting to fix the error (e.g., spelling or capitalization for logging in). Although the program aims to support and be bug-free, they might remain in the program and if they are persistent and affecting the experience. Contact the authors of the program for assistance.



\subsection{Common Login Issues}
Login issues can only arise when the user, faculty, student, or administrator, enters an incorrect username or password. If and when this occurs, a message will be prompted to inform the user that their inputted information is incorrect. It does not provide feedback on whether it is the password or the username.


\subsection{Frequently Asked Question}
\begin{enumerate}
    \item How many times can you attempt to login before it locks me out?
    \begin{itemize}
        \item The login menu will not lock out users if they continue to enter incorrect passwords and usernames.
    \end{itemize}
    \item Do faculty users have access to deleting students privileges
    \begin{itemize}
        \item Faculty users do not have the permission to delete student, only the administrators have access to complete this task.
    \end{itemize}
\end{enumerate}

% \subsection{Error Message \& Solutions (Optional)}